Sweep Z - general experiment analysis.

### 2018-04-03 voltagebudget/analysis/sweep_sigma_analysis.Rmd
Update/cleanup sigma vis Rmd

# sigma scan
exp <- "90"
sigmas <- c("1.0e-9", "5.0e-9", "10.0e-9")

@@

# Ref (Z=0)
exp <- "91"
name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
df <- read_csv(paste(name, sep=","))
df$sigma <- rep(0, nrow(df))
results <- rbind(df, results)

@@

```{r, fig.width=1.9, fig.height=1}
results %>% 
  ggplot(aes(x=V_osc/V_b, y=errors*1e3)) +
  geom_point(size=0.01, alpha=0.01) + 
  theme_classic() +
  facet_grid(.~sigma) +
  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.9, fig.height=1}
results %>% 
  filter(V_osc/V_comp <= 1) %>% 
  filter(n_spikes >0) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
  geom_point(size=0.01, alpha=0.01) + 
  theme_classic() +
  facet_grid(.~sigma) +
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.1, alpha=0.5, color="purple", linetype="dashed") +
  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=5.5, fig.height=2.5}
M1 <- mean(filter(results, sigma == 0)$errors*1e3)
max_N <- max(results$N)

results %>% 
  filter(V_osc/V_comp <= 3) %>%
  filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc/V_b, y=errors*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) + 
  facet_grid(sigma~rank) +
  scale_colour_brewer(palette = "Accent", name="Spike count") +
  labs(x=expression(V[o]/V[b]), y="Error (ms)") +
  geom_hline(yintercept = M1, alpha=0.7, color="black") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="right", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank())

rm(max_N, M1)
```

@@

```{r, fig.width=1.9, fig.height=1}
results %>% 
  # filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_b, y=variances*1e3)) +
  geom_point(size=0.01, alpha=0.01) + 
  theme_classic() +
  facet_grid(.~sigma) +
  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom")
```

```{r, fig.width=1.9, fig.height=1}
results %>% 
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances*1e3)) +
  geom_point(size=0.01, alpha=0.01) + 
  theme_classic() +
  facet_grid(.~sigma) +
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=5.5, fig.height=2.5}
max_N <- max(results$N)

results %>% 
  filter(V_osc/V_comp <= 3) %>%
  filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc/V_b, y=variances*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) + 
  facet_grid(sigma~rank) +
  scale_colour_brewer(palette = "Accent", name="Spike count") +
  labs(x=expression(V[o]/V[b]), y="Variance (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="right", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank())

rm(max_N)
```

@@

```{r, fig.width=1.9, fig.height=1}
M1 = mean(filter(results, sigma == 0)$errors*1e3)
M2 = mean(filter(results, sigma == 0)$variances*1e3)

@@

```{r, fig.width=6.5, fig.height=2.5}
M1 <- mean(filter(results, sigma == 0)$errors*1e3)
M2 <- mean(filter(results, sigma == 0)$variances*1e3)
max_N <- max(results$N)

results %>% 
  filter(V_osc/V_comp <= 3) %>%
  filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
  ggplot(aes(x=errors*1e3, y=variances*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) + 
  facet_grid(sigma~rank) +
  scale_colour_brewer(palette = "Accent", name="Spike count") +
  labs(x="Error (ms)", y="Variance (ms)") +
  geom_vline(xintercept = M1, alpha=0.7, color="black") +
  geom_hline(yintercept = M2, alpha=0.7, color="black") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="right", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank())

rm(max_N, M1)
```

>>>>

# sigma scan
exp <- "97"
# sigmas <- c("1.0e-9", "5.0e-9", "10.0e-9")
sigmas <- c("1.0e-9", "2.0e-9", "3.0e-9", "4.0e-9", "5.0e-9")

@@

# Ref (Z=0)
exp <- "96"
name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
df <- read_csv(paste(name, sep=","))
df$sigma <- rep(0, nrow(df))
results <- rbind(df, results)

@@

```{r, fig.width=1.9, fig.height=1}
results %>% 
  ggplot(aes(x=V_osc/V_b, y=errors*1e3)) +
  geom_point(size=0.01, alpha=0.01) + 
  theme_classic() +
  facet_wrap(~sigma) +
  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.9, fig.height=1.3}
results %>% 
  filter(V_osc/V_comp <= 3) %>% 
  group_by(N, sigma) %>% 
  mutate(norm_errors = errors/max(errors)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_errors)) +
  geom_point(size=0.01, alpha=0.01) + 
  theme_classic() +
  facet_wrap(~sigma) +
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

@@

```{r, fig.width=1.9, fig.height=1.4}
results %>% 
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances*1e3)) +
  geom_point(size=0.01, alpha=0.01) + 
  theme_classic() +
  facet_wrap(~sigma) +
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  # scale_colour_brewer(palette="Greys", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

@@

```{r, fig.width=3, fig.height=1}
M1 = mean(filter(results, sigma == 0)$errors*1e3)
M2 = mean(filter(results, sigma == 0)$variances*1e3)

@@
